{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Models for detecting BHBH, BHNS and NSNS binaries with LISA

### 2021-11-23 paper/tex/sections/appendix.tex

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{fig14_random_simple_galaxy.png}
    \caption{As Fig.~\ref{fig:galaxy_schematic} (right panel), but for the Milky Way model used in \citet{Breivik+2020}.  \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_random_simple_galaxy.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
    \label{fig:simple_mw}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{fig15_mBH_simple_mw_variation.pdf}
    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}b, but for the Milky Way model used in \citet{Breivik+2020}. Dotted lines show the distribution from Fig.~\ref{fig:fiducial_pdf_distributions}b for comparison. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig15_mBH_simple_mw_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:bh_mass_simple_mw}
\end{figure}

@@

\begin{figure}[p]
    \centering
    \includegraphics[height=0.85\textheight]{fig16_formation_channels.pdf}
    \caption{Fraction of each DCO type that is formed through different formation channels for all physics variations. Channels are described in detail in \citet{Broekgaarden+2021}. The classic, single core CEE and double core CEE channels all require at least one common-envelope event whilst only ``only stable'' consists of only stable mass transfer and ``other'' contains the remaining binaries which are mainly formed from case A ``classic'' binaries as well as ``lucky'' supernova kicks that shrink the binary. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig16_formation_channels.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/formation_channels.ipynb}{\faBook}.}
    \label{fig:formation_channels}
\end{figure}

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{fig17_dcos_on_sc_eccentric_colours.png}
    \caption{As the bottom panels of Fig.~\ref{fig:dcos_on_sc}, but without the density distributions and scatter points are coloured by their eccentricity. We show eccentric sources are located in an offshoot below the $30 \unit{kpc}$ around $2 \unit{mHz}$. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig17_dcos_on_sc_eccentric_colours.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/sensitivity_curve.ipynb}{\faBook}.}
    \label{fig:dcos_on_sc_ecc_col}

    \includegraphics[width=0.8\textwidth]{fig18_dco_formation_distributions.pdf}
    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}, but for the properties of the detectable systems at DCO formation. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig18_dco_formation_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:dco_formation_properties}
\end{figure*}

>>>>

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{figD1_random_simple_galaxy.png}
    \caption{As Fig.~\ref{fig:galaxy_schematic} (right panel), but for the Milky Way model used in \citet{Breivik+2020}.  \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/figD1_random_simple_galaxy.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
    \label{fig:simple_mw}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{figD2_mBH_simple_mw_variation.pdf}
    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}b, but for the Milky Way model used in \citet{Breivik+2020}. Dotted lines show the distribution from Fig.~\ref{fig:fiducial_pdf_distributions}b for comparison. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/figD2_mBH_simple_mw_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:bh_mass_simple_mw}
\end{figure}

@@

\begin{figure}[p]
    \centering
    \includegraphics[height=0.85\textheight]{figF1_formation_channels.pdf}
    \caption{Fraction of each DCO type that is formed through different formation channels for all physics variations. Channels are described in detail in \citet{Broekgaarden+2021}. The classic, single core CEE and double core CEE channels all require at least one common-envelope event whilst only ``only stable'' consists of only stable mass transfer and ``other'' contains the remaining binaries which are mainly formed from case A ``classic'' binaries as well as ``lucky'' supernova kicks that shrink the binary. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/figF1_formation_channels.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/formation_channels.ipynb}{\faBook}.}
    \label{fig:formation_channels}
\end{figure}

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{figF2_dcos_on_sc_eccentric_colours.png}
    \caption{As the bottom panels of Fig.~\ref{fig:dcos_on_sc}, but without the density distributions and scatter points are coloured by their eccentricity. We show eccentric sources are located in an offshoot below the $30 \unit{kpc}$ around $2 \unit{mHz}$. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/figF2_dcos_on_sc_eccentric_colours.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/sensitivity_curve.ipynb}{\faBook}.}
    \label{fig:dcos_on_sc_ecc_col}

    \includegraphics[width=0.8\textwidth]{figF3_dco_formation_distributions.pdf}
    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}, but for the properties of the detectable systems at DCO formation. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/figF3_dco_formation_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:dco_formation_properties}
\end{figure*}

### 2021-11-23 paper/tex/sections/variations.tex

In Fig.~\ref{fig:lower_mass_gap_variation}, we show the component mass distribution for all LISA detectable DCOs (BHBHs, BHNSs and NSNSs) for two different remnant mass prescriptions. The grey distribution uses the Fryer \textit{delayed} remnant mass prescription \citep{Fryer+2012}, which is our fiducial assumption (model \modFid{}). This prescription produces compact objects in the lower mass gap ($2.5 \unit{M_{\odot}} \le m \le 5 \unit{M_{\odot}}$) and indeed we find that, of the LISA detectable DCOs, approximately \BHBHatLeastOneLowerMassGapPerc{}\% of BHBHs, \BHNSatLeastOneLowerMassGapPerc{}\% of BHNSs and \NSNSatLeastOneLowerMassGapPerc{}\% of NSNSs have at least one component in the lower mass gap. Overall, weighting by the relative detection rates, this gives that 55\% of our predicted LISA DCO detections would have at least one component in the lower mass gap when using this remnant mass prescription.

Alternatively, the blue curve in Fig.~\ref{fig:lower_mass_gap_variation} shows the same distribution but for the \textit{rapid} remnant mass prescription \citep{Fryer+2012}, which we use in model \modRapid{}. In this case, no compact objects are formed (and therefore, detected) in the lower mass gap. From the stark difference between these models, it is clear that it is difficult at this point to say with any certainty what fraction of systems LISA will detect in the lower mass gap given the highly uncertain formation rate of systems in this mass range.

However, it is important to highlight that \textit{if} DCOs are formed with components in the lower mass gap, LISA \textit{will} be able to detect them. And thus, LISA could be a useful instrument for providing evidence for the existence or non-existence of a lower mass gap based on the mass distribution of detected DCOs.

>>>>

In Fig.~\ref{fig:lower_mass_gap_variation}, we show the component mass distribution for all LISA detectable DCOs (BHBHs, BHNSs and NSNSs) for two different remnant mass prescriptions. The grey distribution uses the Fryer \textit{delayed} remnant mass prescription \citep{Fryer+2012}, which is our fiducial assumption (model \modFid{}). This prescription produces compact objects in the lower mass gap ($2.5 \unit{M_{\odot}} \le m \le 5 \unit{M_{\odot}}$) and indeed we find that, of the LISA detectable DCOs, approximately \BHBHatLeastOneLowerMassGapPerc{}\% of BHBHs, \BHNSatLeastOneLowerMassGapPerc{}\% of BHNSs and \NSNSatLeastOneLowerMassGapPerc{}\% of NSNSs have at least one component in the lower mass gap. Overall, weighting by the relative detection rates, this gives that, in our fiducial model, 55\% of our predicted LISA DCO detections would have at least one component in the lower mass gap when using this remnant mass prescription. This equates to approximately 68 systems being detected in the lower mass gap. Alternatively, the blue curve in Fig.~\ref{fig:lower_mass_gap_variation} shows the same distribution but for the \textit{rapid} remnant mass prescription \citep{Fryer+2012}, which we use in model \modRapid{}. In this case, no compact objects are formed (and therefore, detected) in the lower mass gap.

From the stark difference between these models, it is clear that it is difficult at this point to say with any certainty what fraction of systems LISA will detect in the lower mass gap given the highly uncertain formation rate of systems in this mass range. Indeed, we find that the percentage of detectable systems with at least one component in the lower mass gap varies between approximately 30-70\% (or, in terms of detections, from 15 to 156) for the different model variations. However, it is important to highlight that \textit{if} DCOs are formed with components in the lower mass gap, LISA \textit{will} be able to detect them. And thus, LISA could be a useful instrument for providing constraints on the existence or non-existence of a lower mass gap based on the mass distribution of detected DCOs.
